Preprocessing: filtering

### 2022-08-11 analysis/filtering.Rmd
add funcsions to remove extra notes
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: "Preprocessing: filtering (experiment)"
output: html_notebook
---

```{r setup, include = FALSE}
# set working directory
if (!require("here")) {install.packages("here"); require("here")}
here::i_am("filtering.Rmd")

@@

# Onset
## Detect erroneous trials
```{r, echo = FALSE}
dt_error_onset <- checker(dt_onset, dt_ideal)

@@

# Offset

## Detect erroneous trials
```{r, echo = FALSE}
dt_error_offset <- checker(dt_offset, dt_ideal)

@@

# Checking

>>>>

---
title: "Preprocessing: filtering"
output: html_notebook
---

```{r setup, include = FALSE}
# set chunk option
knitr::opts_chunk$set(echo = FALSE)

# set working directory
if (!require("here")) {install.packages("here"); require("here")}
here::i_am("filtering.Rmd")

@@

# Detect erroneous trials

1) Onset

```{r onset}
dt_error_onset <- checker(dt_onset, dt_ideal)

@@

2) Offset

```{r offset, echo = FALSE}
dt_error_offset <- checker(dt_offset, dt_ideal)

@@

# Manual pitch removal

## Extra notes
1) Onset

```{r extra, include = FALSE}
dt_error_onset$CorrectionNr <- NA

error_extra_onset <- dt_error_onset[Reason == "Extra Notes"]
dt_correct_onset_2 <- data.table()
for (row in 1:nrow(error_extra_onset)){
  current <- dt_onset[SubNr == error_extra_onset$SubNr[row] & TrialNr == error_extra_onset$TrialNr[row]]
  decision = 2 
  correction = 0 # # of correction for reporting stats
  while (decision == 2){
    print(sprintf("SubNr: %s, TrialNr: %s", unique(current$SubNr), unique(current$TrialNr)))
    print("----- First check -----")
    current <- edit(current, dt_ideal)
    print("----- Correction check -----")
    edit(current, dt_ideal)
    decision <- menu(c("y", "n", "other"), title = "Save the current data? (to continue, enter 'n')")
    if (decision == 1){
      correction = correction + 1
      error_extra_onset$CorrectionNr[row] <- correction
      dt_correct_onset_2 <- rbind(dt_correct_onset_2, current[, -c(5:6)])
    } else if (decision == 3){
      error_extra_onset$CorrectionNr[row] <- readline(prompt = "Reason?: ")
    } else if (decision == 2){
      correction = correction + 1
      print("----- Continue correction -----")
    }
  }
}

# export csv
fwrite(dt_correct_onset_2, file = here("filtered", "dt_correct_onset_2.txt"))
```

2) Offset

```{r extra, include = FALSE}
dt_error_offset$CorrectionNr <- NA

error_extra_offset <- dt_error_offset[Reason == "Extra Notes"]
dt_correct_offset_2 <- data.table()
for (row in 1:nrow(error_extra_offset)){
  current <- dt_offset[SubNr == error_extra_offset$SubNr[row] & TrialNr == error_extra_offset$TrialNr[row]]
  decision = 2 
  correction = 0 # # of correction for reporting stats
  while (decision == 2){
    print(sprintf("SubNr: %s, TrialNr: %s", unique(current$SubNr), unique(current$TrialNr)))
    print("----- First check -----")
    current <- edit(current, dt_ideal)
    print("----- Correction check -----")
    edit(current, dt_ideal)
    decision <- menu(c("y", "n", "other"), title = "Save the current data? (to continue, enter 'n')")
    if (decision == 1){
      correction = correction + 1
      error_extra_offset$CorrectionNr[row] <- correction
      dt_correct_offset_2 <- rbind(dt_correct_offset_2, current[, -c(5:6)])
    } else if (decision == 3){
      error_extra_offset$CorrectionNr[row] <- readline(prompt = "Reason?: ")
    } else if (decision == 2){
      correction = correction + 1
      print("----- Continue correction -----")
    }
  }
}

# export csv
fwrite(dt_correct_offset_2, file = here("filtered", "dt_correct_offset_2.txt"))
```
